### 2020-03-25 tex/intro.tex
edit intro

\section{Introduction}
\label{intro}
The NuCypher network ~\cite{egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral  scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
ciphertext encrypted under Alice's public key into ciphertext encrypted under the delegatee's, or Bob's,
public key. This enables the latter to decrypt the data without revealing anything about the
decryption keys or the raw data to the intermediate servers.

Joining the NuCypher network is governed by consensus rules defining the service setup
and the monetary incentives paid to provide the service. In order to join the 
system, Ursula needs to stake an amount of NU tokens for a specific period
which will be released when the pre-specified staking period is over. Alice chooses an
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. As such, the stake value influences the amount of service load an Ursula
may receive. This stake is also used to punish Ursula financially, by revoking part 
of it, when cheating is detected.

@@

\subsection{Monetary Incentives in the NuCypher Network}
Ursulas are rewarded for the re-encryption service by using two sources; 
the first is the service fees collected from the policy or data 
owner Alice, while the second is inflation rewards, i.e., newly minted
NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage 
adoption. It is expected that these rewards will disappear as the token cap is 
reached, similar to other cryptocurrencies out there.

@@

As for fees, Ursula collects the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed their online status.

\subsection{Problems with Current Reward Computation Approach}
The current approach of computing Ursula's inflation rewards and service fees suffers from two
main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation is agnostic to the number of 
requests Ursula serves. Thus an active Ursula who may serve a huge number of 
requests, and one who does not receive any requests (or a
malicious Ursula that does not answer the requests she receives from Bob), will 
both collect the same rewards if they hold identical policies.
\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
can stay offline and not respond to Bobs' requests, and simply come online merely to call the confirm activity
function. This allows Ursula to collect both inflation rewards 
and fees without doing anything, and even worse, it will be able to get her stake back once it unlocks (policies being managed by Ursula will have expired by this point). 
\end{itemize}

\subsection{Proposed Solutions}
We need a provably secure mechanism to be used by Ursula to report the 
number of distinct Bob requests it handled during a specific period, and use this number 
to compute the fees to be collected from Alice. Thus, we call this confirm 
service activity, as opposed to confirm activity that refers to solely being available 
online.

Although we can use the number of served requests to compute the inflation 
rewards as well, this will encourage Ursula to collude with Bob to issue a large
number of requests. If inflation rewards were to be distributed based on the earning of fees (which is desirable, as it would link node subsidization more closely with the network service), this might encourage Ursula to deploy its own Alice(s) 
and Bob(s) to increase the demand, and thus increase its cut of the inflation rewards.

In this document, we introduce several solutions for confirming service activity. 
These solutions differ in the trust, efficiency, interactivity, and resource 
requirements, in addition to their security guarantees. We present each of these 
solutions, where one of them is still a work in progress, discuss the aforementioned
trade-offs and requirements of each of them, with the goal of selecting one of these 
solutions to be adopted in the NuCypher network.

\subsection{Roadmap}
The rest of this document is organized as follows. Section~\ref{threat-network-model} 
outlines the network and threat models adopted by the proposed solutions. 
Section~\ref{prelim} provides an overview of the underlying cryptographic primitives and 
protocols, while the proposed solutions are presented 
in Section~\ref{solutions} with their security and efficiency aspects analyzed in 
Section~\ref{analysis}. Lastly, directions of future work on the confirm activity issue 
are outlined in Section~\ref{future-work}.

>>>>

\section{Introduction}
\label{intro}
The NuCypher network~\cite{egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
public key. This enables the latter to decrypt the data without revealing anything about the
decryption keys or the raw data to the intermediate servers.

Joining the NuCypher network is governed by consensus rules defining the service setup
and the monetary incentives paid to provide the service. In order to join the 
system, Ursula needs to stake an amount of NU tokens for a specific period
which will be released when the pre-specified staking period is over. Alice chooses an
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. Therefore, the stake value influences the amount of service load an Ursula
may receive. This stake is also used to punish Ursula financially, by revoking part 
of it, if it cheats and this cheating is detected.

@@

\subsection{Monetary Incentives in the NuCypher Network}
Ursulas are rewarded for the re-encryption service by using two sources; 
the first is the service fees collected from the policy  
owner Alice, while the second is inflation rewards, i.e., newly minted
NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage 
adoption. It is expected that these rewards will disappear as the token cap is 
reached, similar to other cryptocurrencies out there.

@@

As for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed its online status.

\subsection{Problems with Current Reward Computation Approach}
The current approach of computing Ursula's inflation rewards and service fees suffers from two
main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation (both fees and inflation rewards) is agnostic to the number of 
requests Ursula serves. Thus an active Ursula who may serve a huge number of 
requests, and one who does not receive any requests (or a
malicious/lazy Ursula that does not answer the requests she receives from Bob), will 
both collect the same amount of rewards if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
can stay offline and not respond to Bobs' requests, and simply come online merely to call the confirm activity
function. This allows Ursula to collect both inflation rewards 
and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks (i.e., when policies being managed by Ursula expire). 
\end{itemize}

\subsection{Overview}
The confirm activity problem is defined differently based on the stage of the 
NuCypher network. In early network operation, when inflation rewards are 
still distributed, we are concerned with the availability of Ursulas and being willing to 
serve all requests coming from Bob. In other words, regardless of the number of 
requests served, the rewards value will be computed based on the period during which Ursula 
is online and well-behaving. While in later stages, when inflation rewards disappear 
and only fees exist, confirm activity will be tied to providing the re-encryption 
service in the sense that the payment will be computed based on the amount of 
service provided. Thus, Ursula needs to confirm its activity by proving that she served 
a given number of distinct re-encryption requests during a give period. To make the distinction 
clear, we refer to the first as confirm availability, and for the second as confirm 
service activity.

In terms of the underlying threat model, for both problem definitions we do not consider collusion 
between Bob and Ursula as a practical threat. This means that cases of Bob pretending  
that he got service from Ursula (while no service is delivered) is not an issue (we do not 
suspect this will be of any importance and there is no motivation to do it given that 
the work Ursula does for re-encryption is minimal).

In this document, we introduce several solutions for both forms of confirming activity. 
These solutions differ in the trust, efficiency, interactivity, and resource 
requirements, in addition to their security guarantees. We divide the document into 
two parts, the first is about confirm availability, while the second is about confirm 
service activity. We present each of our solutions, discuss the aforementioned
trade-offs and requirements of each of them, with the goal of selecting one of these 
solutions to be adopted in each operational stage of the NuCypher network.
